\documentclass{article}

\begin{document}
    \title{Information Sheet \\
    An investigation into the effectiveness and impact of a Continuous Delivery pipeline upon university-level games development teams.}
    \author{Frost Donovan}

    \maketitle

    \section{Introduction}
        Hello, I am Frost Donovan, a third year Computing For Games student who has been a Producer throughout my group projects. I can be contacted at \textbf{FrostBDonovan@gmail.com}. The supervisor for this research is Dr Michael Scott, who can be contacted at \textbf{michael.scott@falmouth.ac.uk}.
        The purpose of this dissertation is to investigate the effect of a Continuous Delivery pipeline can have upon student game development teams. In industry, these pipelines are used to increase the consistency of available builds, as well as the quality and reliability of those builds. 

        Potential benefits for participating in this research are:
        \begin{itemize}
            \item A game build that is automatically produced every night and is then available to be downloaded. This will be built from your main branch on Git.
            \item This allows an up-to-date build to always be accessible, as well as making it easy to download historic builds.
            \item This will also flag any errors that would prevent a build being made, or any problems that would cause any unit tests to fail. 
        \end{itemize}

    \section{Commitment \& risk}
        Participants will be required to fill out a short, 7 question form every two weeks. All questions that will be on the form are included on the next page.
        The entire team will need to consent to this tool being run in order for a team to be eligible, although only a \textit{majority} of the team members will need to commit to filling out the survey every two weeks. Ideally, every member of the team would fill out the survey. 
        \\ \\
        A team's academic supervisor will also be required to fill out a short form every two weeks, so they will also need to consent \& commit to this. Again, all the questions for supervisors are included on the next page. 
        \\ \\
        There will also be a short, free form interview at the conclusion of the research.
        
        \newpage

        \subsubsection*{For Students}
        \begin{itemize}
            \item Do you consent to this data to be stored and used as part of a dissertation? Yes/ No (Must be answered Yes to allow submission)
            \item On a scale of 1 – 10, how confident do you feel in being able to deliver everything within the projects scope by the end of the project? Why?
            \item On a scale of 1 – 10, how confident do you feel that you understand the current state of the project as a whole? Why?
            \item On a scale of 1 – 10, how well do you understand how your current tasks contribute to the project as a whole? Very briefly describe how your current tasks contribute to the project as a whole.
            \item How often does the team refine the scope of the project?
            \item Do you have any other feedback regarding the CD pipeline or its effect on you or the team?
            \item How many times have you done play testing in the last two weeks, both internally and externally?
        \end{itemize}

        \subsubsection*{For Supervisors}
        \begin{itemize}
            \item Do you consent to this data to be stored and used as part of a dissertation? Yes/ No (Must be answered Yes to allow submission)
            \item On a scale of 1 – 10, how confident do you feel that your team will deliver a new, working build the next time they meet with you? Why?
            \item On a scale of 1 – 10, how confident do you feel that your team will be able to complete everything within their planned scope by the end of the project? Why?
            \item Has the use of a CD pipeline had any noticeable impact upon the team? If yes, please expand on what this impact has been.
            \item Do you have any other feedback regarding the CD pipeline or its effect on you or the team? (This is to facilitate any feedback not covered by the above questions)
        \end{itemize}
        
        \newpage

    \section{Remuneration \& withdrawal}
        There will be no form or renumeration offered, although teams are of course free to use any builds produced by the Continuous Delivery tool for their game for any purpose.
        \\ \\
        Participants are free to withdraw from the research at any time by emailing Frost Donovan at \textbf{FrostBDonovan@gmail.com}. 
        \\ \\
        Participants may also request a copy of the research paper upon completion of the research project by emailing Frost Donovan at \textbf{FrostBDonovan@gmail.com}.
        
    \section{Declaration of confidentiality}
        Any data collected will be anonymised and stored only for the duration of the research under GDPR compliant conditions.

\end{document}